% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
\par{
I'm an economist and an R-enthusiast. I'm currently working at the Monitoring and Evaluation unity at Transforma Uruguay. Transforma Uruguay is a government institution for the implementation of the National Plan for Productive Transformation and Competitiveness. Part of my role is to process data from policies to monitor them and also to offer input to decision making. We develop Shiny apps for policymakers in order to make the data exploration and visualization more fruitful such as one to geographically explore government centralized purchases and re-assign them, taking into consideration a new law which reserves a proportion of those purchases to rural producers and another one to know about the policies included in the Plan, their characteristics and download the data. Also, I have developed an R-package with the brand identity to create unified ggplot graphs, shinydashboards and Rmarkdown reports for the institution. In addition, I'm giving R-from-scratch workshops for the office (from communicators to people with degree in International Relations) and we're planning to expand this courses for the nucleated institutions and agencies in Transforma Uruguay so we have an homogeneous workflow. I'm also involved in R-Ladies, a worldwide organization whose mission is to promote gender diversity in the R community, as co-organizer of the Montevideo chapter. I'm particularly interested in data visualization for science and social causes communication, I strongly believe in the power of a good visualization to democratize knowledge. Therefore, I have an active Twitter presence where I enjoy making threads to explain  papers and to spread data about particular causes: International Women's Day and International Day for the Elimination of Violence against Women, among others.

}